Hydrodynamics of a Semipermeable Vesicle Under Flow and Confinement

### 2020-12-30 vesicle_code/docs/permeableVes/main.tex
yny

\begin{abstract}
Lipid bilayer membranes have a native (albeit small) permeability for
water molecules. As long as the bilayer structure stays intact
without poration or rupture under load, the water influx/efflux is
often assumed to be negligible in the absence of a gradient of osmotic
stress. In this work we use boundary integral simulations to
investigate the effects of water permeability on the hydrodynamics of
a vesicle under various flows and confinement configurations. Coupling
the membrane permeability with membrane elastic stress, tension, and
mechanical stress in the framework of Helfrich free energy, we
illustrate that, in the absence of an osmotic stress gradient, a giant
unilamellar vesicle may be significantly affected by water
influx/efflux over a sufficiently long time or under a strong
confinement. Our simulation results quantify the conditions for water
permeation to be negligible in terms of the time scales, flow strength
of an external flow, and degree of confinement. These results shed
light on how microfluidic confinement can be utilized to estimate
membrane permeability.
%
%osmotic stress gradient 
%We describe a mathematical model for a semipermeable vesicle and derive
%  a boundary integral equation formulation for simulating its
%  hydrodynamics.  
%
%Please provide an abstract of no more than 250 words in a single paragraph. Abstracts should explain to the general reader the major contributions of the article. References in the abstract must be cited in full within the abstract itself and cited in the text.
\end{abstract}

@@

The lipid bilayer membrane is permeable to water and water-soluble
molecules~\cite{Dick1964_JTB, FettiplaceHaydon1980_PhysRev,
DeamerBramhall1986_ChemPhysLipids, Grafmueller2019_ABLS}. 
%
%In the presence of an osmotic gradient across the membrane (such as a contrast in the concentration of an impermeable solute), water flows against the osmotic gradient  to neutralize the osmolarity. 
%
Without aquaporins or other membrane channels that promote water
permeability, the intrinsic water permeability is known to depend on the
temperature, lipid composition~\cite{OlbrichRawiczNeedhamEtAl2000_BJ}, 
%\todo[inline]{Same reference twice?} 
and the hydration of
the membrane~\cite{MarrinkBerendsen1994_JPhysChem}. In the red blood
cell membrane, aquaporin-1 channels give rise to a much higher water
permeability of approximately $1.8\times 10^{-2}$ cm/s in
erythrocytes~\cite{YangMaVerkman2001_JBC} while the intrinsic water
permeability of a lipid bilayer membrane is in the range of
$10^{-4}$--$10^{-3}$ cm/s~\cite{ThompsonHuang1966_ANYAS,
FettiplaceHaydon1980_PhysRev, Grafmueller2019_ABLS, Dimova2020_GVB,
BhatiaRobinsonDimova2020_SoftMatt}. 
%
%The swelling/shrinking of a cell is inevitably coupled to changes in
%membrane tension and deformation. Under a strong confinement (such as
%going through a microcapillary or submicron slit),  the transmembrane
%water flow may have comparable contributions from both osmotic and
%mechanical stresses
%\cite{StrokaJiangChenEtAl2014_Cell,LiMoriSun2015_PRL,yao-mor2017}.  
Molecular dynamic (MD) simulations show that a stretched red blood cell
membrane porates when the membrane tension reaches the order of $2$--$4$
mN/m (\cite{RazizadehNikfarPaulLiu2020_BJ} and references therein),
giving rise to enhanced membrane permeability to both water and
macromolecules. Consequently, as long as the lipid bilayer membrane
remains intact (no poration or rupture), red blood cells and vesicles
are assumed to be of the same volume throughout experiments of durations
no longer than tens of minutes.
%
%membrane poration is inevitable when membrane tension is of the order
%of $2-4$ mN/m (\cite{RazizadehNikfarPaulLiu2020_BJ} and references
%therein). 
%%The CGMD results further show that a stretched RBC membrane may have pores that might contribute to transmembrane transport of both water and ATP molecules \cite{RazizadehNikfarPaulLiu2020_BJ}. 
%Thus an important outstanding question in stress-induced ATP release of
%highly deformed RBCs is if there is any transmembrane flow when RBCs
%release ATP as they experience large mechanical load due to confinement
%or large shear stress?  To address such question, the first step we
%take is to focus on the permeable water flux induced by mechanical
%stress.
%%
%%RBCs are known to release ATP under large deformation and microfluidic experiments have been used to study the correlation between RBC deformation and ATP release \cite{Wan2008_PNAS,ForsythWan2011_PNAS,ZhangShenHoganBarakatMisbah2018_BJ}.
%%
%%Why is it interesting to study the dynamics of a semipermeable membrane induced by mechanical stress/confinement?
%%
%%The osmolarity-induced water flux has been well studied, while mechanical pressure may also contribute to the permeable water flow \cite{yao-mor2017}.
%%The response of a cell to an osmotic gradient is inevitably both mechanical (tension redistribution and shape change) and chemical (water flux across the membrane).  
Under what condition is this a good assumption? Do vesicles conserve
volume over hours under flow? What is the dynamic consequence when water
influx/efflux affects the membrane hydrodynamics? To answer these
questions, we investigate the balance between hydrodynamics, tension,
and elasticity of a semipermeable membrane under various flowing
conditions and confinement. 
%Specifically our numerical simulations yield the quantification of the
%time scale and length scale over which water permeation becomes
%important.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htp]
  \centering
  \includegraphics[width=0.5\textwidth]{figures/schematic.pdf}
  \caption{\label{fig:sketch} Schematics showing the effects of
  semipermeability on vesicle hydrodynamics in various configurations.
  The slipper in (a) is the steady-state shape of a semipermeable
  vesicle in a Poiseuille flow.}
\end{figure}

\section*{Formulation}
We consider a two-dimensional semipermeable vesicle (permeable only to
water) suspended in a viscous fluid (Figure~\ref{fig:sketch}). To focus
on the effect of water flow on vesicle hydrodynamics in various
conditions, we assume the fluid is the same inside and outside the
vesicle membrane. On the membrane the permeable water flux gives rise to
a difference between the fluid velocity ${\uu}({\xx}\in \gamma)$ and the
membrane velocity $\dot{\xx}$~\cite{yao-mor2017}:
\begin{align}
  \uu - \dot{\xx} = - k_w (R T \triangle c + \ff_\mathrm{mem} \cdot \nn) \nn, \qquad
  \xx \in \gamma,
\end{align}
where $\gamma$ denotes the membrane boundary with an outward normal
$\nn$ (Figure~\ref{fig:sketch}), $k_w$ is the water permeability, $R$ is
the ideal gas constant, $T$ is the temperature ($^{\circ}$K), $\triangle
c$ is contrast in a solute concentration (mol/volume), and
$\ff_\mathrm{mem}$ is the membrane stress that consists of both bending
$ \ff_\mathrm{ben}= -k_b \xx_{ssss}$ and tension
$\ff_\mathrm{ten}=(\sigma \xx_s)_s$ ($s$ is the arclength along the
membrane, see Supplementary Material). Using $k_w\sim 10^{-12}$
m$^2$s/kg (typical of mammalian cell membranes~\cite{LiMoriSun2015_PRL})
and an osmolarity $\triangle c = 0.1$ mol/L (consistent with the osmotic
forces in vesicle aspiration
experiments~\cite{OlbrichRawiczNeedhamEtAl2000_BJ}), the corresponding
water flow is of the order $v_\mathrm{o}=0.1 \mu$m/s. Assuming that the
membrane bending stiffness $k_b = 10^{-19}$J, a membrane tension
$10^{-3}$N/m (one tenth of the lysis tension), and a characteristic
length scale of $10^{-6}$m, the tension contribution ($v_\mathrm{t}$)
and elastic stress contribution ($v_\mathrm{e}$) to the permeable water
flow can be scaled to $v_\mathrm{o}$ as
$v_\mathrm{o}:v_\mathrm{t}:v_\mathrm{e}=10^{0}:10^{-2}:10^{-6}$.
Furthermore, we note that in the absence of an osmotic stress, the water
permeable flow can be significant when the membrane tension is large due
to the external stress such as the hydrodynamic stress due to an
external flow or confinement. In the following we will explore both.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Semipermeable Vesicle in a Narrow Channel (Stenosis)}
Cells experience stretching and release messengers when they pass
through capillary vessels~\cite{Wan2008_PNAS, ForsythWan2011_PNAS,
Pak2015_PNAS}.  Many cells exhibit extraordinary flexibility as they go
through narrow channels~\cite{AuStoreyMoore2016_PNAS}, and adjustment of
area to volume ratio may be a key factor for a successful passage.  Here
we quantify the effect of water permeability on a vesicle going through
a stenosis (a long microfluidic channel with a width smaller than the
cell radius).  Based on the findings in~\cite{abk-fai-sto2006}, we first
examine the effect of semipermeability on the pressure fluctuation
across a stenosed geometry. In this experiment, a pressure drop is used
to squeeze a red blood cell through a constriction with diameter $5\mu$m
and length $45\mu$m. We set up a similar computational geometry with a
Poiseuille flow imposed at the inlet and outlet
(Figure~\ref{fig:stenosisComposite}(a)). The flow velocity $U_{max} =
1000 \mu$m/s is maintained at the inlet and outlet and is chosen so that the residency time of the vesicle in the
stenosis channel is $t_R \approx 0.5$s which agrees with the
experimental results~\cite{abk-fai-sto2006}. When the red blood cell
enters the channel, an increase in the pressure drop is required to
maintain a constant flow rate, and the difference in the pressure drop
is called the excess pressure.

@@

@@

\begin{figure*}[htp]
  \ifTikz
  \input{figures/stenosisComposite.tikz}
  \else
  \includegraphics{figures/stenosisComposite.pdf}
  \fi
  \caption{\label{fig:stenosisComposite} (a): A semipermeable vesicle
  passing through a constricted geometry similar to the experimental
  device in~\cite{abk-fai-sto2006}. (b): A semipermeable vesicle passing
  through a constricted geometry that is over five times longer. (c):
  The excess pressure of an impermeable and semipermeable vesicle in the
  short geometry in (a). (d): The reduced area of the semipermeable
  vesicles in the geometries in (a) and (b) as a function of the
  vesicles' center of mass. The $x$-axis is scaled by $1/L$ where $L$ is
  half the length of the constriction. (e) The reduced area of the
  semipermeable vesicles in the geometries in (a) and (b) as a function
  of time. The time axis is scaled by $1/t_R$ where $t_R$ is the
  residency time. In parts (c) and (d), the dashed lines correspond to
  the locations of the inlet and outlet. In part (e), the dashed lines
  correspond to the times that the vesicle enters and exits the
  constriction. The colored vesicles show the tension distribution in
  N/m of the circled vesicles. Throughout the entire simulation, these
  vesicle configurations have the largest tension.}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Semipermeable Vesicle in a Contracting Geometry} 
\begin{figure}[htp]
  \centering
  \ifTikz
  \input{figures/contractingComposite.tikz}
  \else
  \includegraphics{figures/contractingComposite.pdf}
  \fi
  \caption{\label{fig:contractingComposite} A contracting geometry
  similar to the experimental device in~\cite{wu2015critical}. The
  channel width varies from $18\mu$m to $1.8\mu$m, and it repeats every
  $45\mu$m. The fluid flux along the red regions is into the vesicle,
  and the fluid flux along the blue regions is out of the vesicle.
  (a--c): The ability for a semipermeable vesicle to pass through the
  contraction depends on the semipermeability rate. (d--f): The ability
  for a semipermeable vesicle to pass through the contraction depends
  on the flow rate. The colored vesicles show the tension distribution
  in N/m of the circled vesicles. Throughout the entire simulation,
  these vesicle configurations have the largest tension.}
\end{figure}
Squeezing a cell or an elastic vesicle through a slit in microfluidics
has gained popularity for its application in stress-induced release of
macromolecules~\cite{ShareiEtAl2013_PNAS, Pak2015_PNAS,
ZhangShenHoganBarakatMisbah2018_BJ, LuoBai2019_PoF}. Red blood cells go
through submicron slits many times during their lifetime, and such
process selects healthy, flexible red blood cells to
survive~\cite{wu2015critical,LuPeng2019_PoF}. Here we investigate the
role of membrane permeability to water when a semipermeable vesicle is
squeezed through a contracting microfluidic channel similar
to~\cite{wu2015critical}, where the width of the channel gradually
decreases from $18 \mu$m to $1.8 \mu$m. The channel then immediately
opens again to $18 \mu$m (Figure~\ref{fig:contractingComposite}). A
Poiseuille flow is imposed at the inlet and outlet with a constant
maximum flow rate of $U_{\max}$. We initialize a semipermeable vesicle
with $\alpha = 0.65$ that spans $10 \mu$m of the total channel width and
investigate the effects of the membrane permeability to water and the
maximum flow velocity on whether a vesicle can successfully pass through
the slit. We color the vesicle according to the sign of its flux---red
for influx and blue for efflux.

@@

\begin{figure}[htp]
  \ifTikz
  \input{figures/contractingComposite2.tikz}
  \else
  \includegraphics{figures/contractingComposite2.pdf}
  \fi
  \caption{\label{fig:contractingComposite2} Vesicle reduced area and
  velocity vs.~time. Permeability rate is $\beta = 10^{-3}$ and maximum
  velocity is $18\mu$m/s. (a): A semipermeable vesicle passing through
  six periods of the contracting geometry. (b): The reduced area with
  the marks representing shapes in (a). (c): The vesicle velocity with
  the marks representing shapes in (a). In (b) and (c), the bottom
  x-axis is the $x$-coordinate of the center of mass, and the upper
  x-axis is time. The colored vesicles show the tension distribution in
  N/m of the circled vesicles. Throughout the entire simulation, these
  vesicle configurations have the largest tension.}
\end{figure}

>>>>

\begin{abstract}
Lipid bilayer membranes have a native (albeit small) permeability for
water molecules. Provided that the bilayer structure stays intact
without membrane poration or rupture under load, the water influx/efflux is
often assumed negligible in the absence of a gradient of osmotic
stress. 
%
In this work we focus on physical regimes where the membrane tension is below the critical value for membrane poration, and use boundary integral simulations to
investigate the effects of native water permeability on the hydrodynamics of
a vesicle under various flows and confinement configurations. 
%
Coupling the membrane permeability with membrane elastic stress, tension, and
mechanical stress in the framework of Helfrich free energy, we
illustrate that, in the absence of an osmotic stress gradient, a giant
unilamellar vesicle may be significantly affected by water
influx/efflux over a sufficiently long time or under a strong
confinement. Our simulation results quantify the conditions for water
permeation to be negligible in terms of the time scales, flow strength
of an external flow, and degree of confinement. These results shed
light on how microfluidic confinement can be utilized to estimate
membrane permeability.
%
%osmotic stress gradient 
%We describe a mathematical model for a semipermeable vesicle and derive
%  a boundary integral equation formulation for simulating its
%  hydrodynamics.  
%
%Please provide an abstract of no more than 250 words in a single paragraph. Abstracts should explain to the general reader the major contributions of the article. References in the abstract must be cited in full within the abstract itself and cited in the text.
\end{abstract}

@@

The lipid bilayer membrane is permeable to water and water-soluble
molecules~\cite{Dick1964_JTB, FettiplaceHaydon1980_PhysRev,
DeamerBramhall1986_ChemPhysLipids, Grafmueller2019_ABLS}. 
%
%In the presence of an osmotic gradient across the membrane (such as a contrast in the concentration of an impermeable solute), water flows against the osmotic gradient  to neutralize the osmolarity. 
%
Without aquaporins or other membrane channels that promote water
permeability, the intrinsic water permeability is known to depend on the
temperature, lipid composition~\cite{OlbrichRawiczNeedhamEtAl2000_BJ}, 
%\todo[inline]{Same reference twice?} 
and the hydration of
the membrane~\cite{MarrinkBerendsen1994_JPhysChem}. In the red blood
cell membrane, aquaporin-1 channels give rise to a much higher water
permeability of approximately $1.8\times 10^{-2}$ cm/s in
erythrocytes~\cite{YangMaVerkman2001_JBC} while the intrinsic water
permeability of a lipid bilayer membrane is in the range of
$10^{-4}$--$10^{-3}$ cm/s~\cite{ThompsonHuang1966_ANYAS,
FettiplaceHaydon1980_PhysRev, Grafmueller2019_ABLS, Dimova2020_GVB,
BhatiaRobinsonDimova2020_SoftMatt}. 
%
%The swelling/shrinking of a cell is inevitably coupled to changes in
%membrane tension and deformation. Under a strong confinement (such as
%going through a microcapillary or submicron slit),  the transmembrane
%water flow may have comparable contributions from both osmotic and
%mechanical stresses
%\cite{StrokaJiangChenEtAl2014_Cell,LiMoriSun2015_PRL,yao-mor2017}.  
Molecular dynamic (MD) simulations show that a stretched red blood cell
membrane porates when the membrane tension reaches the order of $2$--$4$
mN/m (\cite{RazizadehNikfarPaulLiu2020_BJ} and references therein),
giving rise to enhanced membrane permeability to both water and
macromolecules. Consequently, as long as the lipid bilayer membrane
remains intact (no poration or rupture), red blood cells and vesicles
are assumed to be of the same volume throughout experiments of durations
no longer than tens of minutes.
%
%membrane poration is inevitable when membrane tension is of the order
%of $2-4$ mN/m (\cite{RazizadehNikfarPaulLiu2020_BJ} and references
%therein). 
%%The CGMD results further show that a stretched RBC membrane may have pores that might contribute to transmembrane transport of both water and ATP molecules \cite{RazizadehNikfarPaulLiu2020_BJ}. 
%Thus an important outstanding question in stress-induced ATP release of
%highly deformed RBCs is if there is any transmembrane flow when RBCs
%release ATP as they experience large mechanical load due to confinement
%or large shear stress?  To address such question, the first step we
%take is to focus on the permeable water flux induced by mechanical
%stress.
%%
%%RBCs are known to release ATP under large deformation and microfluidic experiments have been used to study the correlation between RBC deformation and ATP release \cite{Wan2008_PNAS,ForsythWan2011_PNAS,ZhangShenHoganBarakatMisbah2018_BJ}.
%%
%%Why is it interesting to study the dynamics of a semipermeable membrane induced by mechanical stress/confinement?
%%
%%The osmolarity-induced water flux has been well studied, while mechanical pressure may also contribute to the permeable water flow \cite{yao-mor2017}.
%%The response of a cell to an osmotic gradient is inevitably both mechanical (tension redistribution and shape change) and chemical (water flux across the membrane).  
Under what condition is this a good assumption? Do vesicles conserve
volume over hours under flow? What is the dynamic consequence when water
influx/efflux affects the membrane hydrodynamics? To answer these
questions, we investigate the balance between hydrodynamics, tension,
and elasticity of a semipermeable membrane under various flowing
conditions and confinement, see Figure~\ref{fig:sketch}.
%Specifically our numerical simulations yield the quantification of the
%time scale and length scale over which water permeation becomes
%important.

\begin{figure}[htp]
  \centering
  \includegraphics[width=0.5\textwidth]{figures/schematic.pdf}
  \caption{\label{fig:sketch} Schematics showing the effects of
  semipermeability on vesicle hydrodynamics in various configurations. 
  The lipid bilayer membrane (modeled as an interface $\gamma$ of zero thickness and an outward normal $\nn$) 
  is permeable to water molecules, depending on the mechanical normal stress balance on the membrane.
  The slipper in (a) is the steady-state shape of a semipermeable
  vesicle in a Poiseuille flow.}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Formulation}
We consider a two-dimensional semipermeable vesicle (permeable only to
water) suspended in a viscous fluid (Figure~\ref{fig:sketch}). To focus
on the effect of water flow on vesicle hydrodynamics in various
conditions, we assume the fluid is the same inside and outside the
vesicle membrane. On the membrane the permeable water flux gives rise to
a difference between the fluid velocity ${\uu}({\xx}\in \gamma)$ and the
membrane velocity $\dot{\xx}$~\cite{yao-mor2017}:
\begin{align}
  \uu - \dot{\xx} = - k_w (R T \triangle c + \ff_\mathrm{mem} \cdot \nn) \nn, \qquad
  \xx \in \gamma,
\end{align}
where $\gamma$ denotes the membrane boundary with an outward normal
$\nn$ (Figure~\ref{fig:sketch}), $k_w$ is the water permeability, $R$ is
the ideal gas constant, $T$ is the temperature ($^{\circ}$K), $\triangle
c$ is contrast in a solute concentration (mol/volume), and
$\ff_\mathrm{mem}$ is the membrane stress that consists of both bending
$ \ff_\mathrm{ben}= -k_b \xx_{ssss}$ and tension
$\ff_\mathrm{ten}=(\sigma \xx_s)_s$ ($s$ is the arclength along the
membrane, see Supplementary Material). Using $k_w\sim 10^{-12}$
m$^2$s/kg (typical of mammalian cell membranes~\cite{LiMoriSun2015_PRL})
and an osmolarity $\triangle c = 0.1$ mol/L (consistent with the osmotic
forces in vesicle aspiration
experiments~\cite{OlbrichRawiczNeedhamEtAl2000_BJ}), the corresponding
water flow is of the order $v_\mathrm{o}=0.1 \mu$m/s. Assuming that the
membrane bending stiffness $k_b = 10^{-19}$J, a membrane tension
$10^{-3}$N/m (one tenth of the lysis tension), and a characteristic
length scale of $10^{-6}$m, the tension contribution ($v_\mathrm{t}$)
and elastic stress contribution ($v_\mathrm{e}$) to the permeable water
flow can be scaled to $v_\mathrm{o}$ as
$v_\mathrm{o}:v_\mathrm{t}:v_\mathrm{e}=10^{0}:10^{-2}:10^{-6}$.
Furthermore, we note that in the absence of an osmotic stress, the water
permeable flow can be significant when the membrane tension is large due
to the external stress such as the hydrodynamic stress due to an
external flow or confinement. In the following we will explore both.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Semipermeable Vesicle in a Narrow Channel (Stenosis)}
 \begin{figure*}[htp]
  \ifTikz
  \input{figures/stenosisComposite.tikz}
  \else
  \includegraphics{figures/stenosisComposite.pdf}
  \fi
  \caption{\label{fig:stenosisComposite} (a): A semipermeable vesicle
  passing through a constricted geometry similar to the experimental
  device in~\cite{abk-fai-sto2006}. (b): A semipermeable vesicle passing
  through a constricted geometry that is over five times longer. (c):
  The excess pressure of an impermeable and semipermeable vesicle in the
  short geometry in (a). (d): The reduced area of the semipermeable
  vesicles in the geometries in (a) and (b) as a function of the
  vesicles' center of mass. The $x$-axis is scaled by $1/L$ where $L$ is
  half the length of the constriction. (e) The reduced area of the
  semipermeable vesicles in the geometries in (a) and (b) as a function
  of time. The time axis is scaled by $1/t_R$ where $t_R$ is the
  residency time. In parts (c) and (d), the dashed lines correspond to
  the locations of the inlet and outlet. In part (e), the dashed lines
  correspond to the times that the vesicle enters and exits the
  constriction. The colored vesicles show the tension distribution in
  N/m of the circled vesicles. Throughout the entire simulation, these
  vesicle configurations have the largest tension.}
\end{figure*}

Cells experience stretching and release messengers when they pass
through capillary vessels~\cite{Wan2008_PNAS, ForsythWan2011_PNAS,
Pak2015_PNAS}.  Many cells exhibit extraordinary flexibility as they go
through narrow channels~\cite{AuStoreyMoore2016_PNAS}, and adjustment of
area to volume ratio may be a key factor for a successful passage.  Here
we quantify the effect of water permeability on a vesicle going through
a stenosis (a long microfluidic channel with a width smaller than the
cell radius).  Based on the findings in~\cite{abk-fai-sto2006}, we first
examine the effect of semipermeability on the pressure fluctuation
across a stenosed geometry. In this experiment, a pressure drop is used
to squeeze a red blood cell through a constriction with diameter $5\mu$m
and length $45\mu$m. We set up a similar computational geometry with a
Poiseuille flow imposed at the inlet and outlet
(Figure~\ref{fig:stenosisComposite}(a)). The flow velocity $U_{max} =
1000 \mu$m/s is maintained at the inlet and outlet and is chosen so that the residency time of the vesicle in the
stenosis channel is $t_R \approx 0.5$s which agrees with the
experimental results~\cite{abk-fai-sto2006}. When the red blood cell
enters the channel, an increase in the pressure drop is required to
maintain a constant flow rate, and the difference in the pressure drop
is called the excess pressure.

@@

\begin{figure}[htp]
  \centering
  \ifTikz
  \input{figures/contractingComposite.tikz}
  \else
  \includegraphics{figures/contractingComposite.pdf}
  \fi
  \caption{\label{fig:contractingComposite} A contracting geometry
  similar to the experimental device in~\cite{wu2015critical}. The
  channel width varies from $18\mu$m to $1.8\mu$m, and it repeats every
  $45\mu$m. The fluid flux along the red regions is into the vesicle,
  and the fluid flux along the blue regions is out of the vesicle.
  (a--c): The ability for a semipermeable vesicle to pass through the
  contraction depends on the semipermeability rate. (d--f): The ability
  for a semipermeable vesicle to pass through the contraction depends
  on the flow rate. The colored vesicles show the tension distribution
  in N/m of the circled vesicles. Throughout the entire simulation,
  these vesicle configurations have the largest tension.}
\end{figure}

@@

%\begin{figure*}[htp]
%  \ifTikz
%  \input{figures/stenosisComposite.tikz}
%  \else
%  \includegraphics{figures/stenosisComposite.pdf}
%  \fi
%  \caption{\label{fig:stenosisComposite} (a): A semipermeable vesicle
%  passing through a constricted geometry similar to the experimental
%  device in~\cite{abk-fai-sto2006}. (b): A semipermeable vesicle passing
%  through a constricted geometry that is over five times longer. (c):
%  The excess pressure of an impermeable and semipermeable vesicle in the
%  short geometry in (a). (d): The reduced area of the semipermeable
%  vesicles in the geometries in (a) and (b) as a function of the
%  vesicles' center of mass. The $x$-axis is scaled by $1/L$ where $L$ is
%  half the length of the constriction. (e) The reduced area of the
%  semipermeable vesicles in the geometries in (a) and (b) as a function
%  of time. The time axis is scaled by $1/t_R$ where $t_R$ is the
%  residency time. In parts (c) and (d), the dashed lines correspond to
%  the locations of the inlet and outlet. In part (e), the dashed lines
%  correspond to the times that the vesicle enters and exits the
%  constriction. The colored vesicles show the tension distribution in
%  N/m of the circled vesicles. Throughout the entire simulation, these
%  vesicle configurations have the largest tension.}
%\end{figure*}
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Semipermeable Vesicle in a Contracting Geometry} 
\begin{figure}[htp]
  \ifTikz
  \input{figures/contractingComposite2.tikz}
  \else
  \includegraphics{figures/contractingComposite2.pdf}
  \fi
  \caption{\label{fig:contractingComposite2} Vesicle reduced area and
  velocity vs.~time. Permeability rate is $\beta = 10^{-3}$ and maximum
  velocity is $18\mu$m/s. (a): A semipermeable vesicle passing through
  six periods of the contracting geometry. (b): The reduced area with
  the marks representing shapes in (a). (c): The vesicle velocity with
  the marks representing shapes in (a). In (b) and (c), the bottom
  x-axis is the $x$-coordinate of the center of mass, and the upper
  x-axis is time. The colored vesicles show the tension distribution in
  N/m of the circled vesicles. Throughout the entire simulation, these
  vesicle configurations have the largest tension.}
\end{figure}

Squeezing a cell or an elastic vesicle through a slit in microfluidics
has gained popularity for its application in stress-induced release of
macromolecules~\cite{ShareiEtAl2013_PNAS, Pak2015_PNAS,
ZhangShenHoganBarakatMisbah2018_BJ, LuoBai2019_PoF}. Red blood cells go
through submicron slits many times during their lifetime, and such
process selects healthy, flexible red blood cells to
survive~\cite{wu2015critical,LuPeng2019_PoF}. Here we investigate the
role of membrane permeability to water when a semipermeable vesicle is
squeezed through a contracting microfluidic channel similar
to~\cite{wu2015critical}, where the width of the channel gradually
decreases from $18 \mu$m to $1.8 \mu$m. The channel then immediately
opens again to $18 \mu$m (Figure~\ref{fig:contractingComposite}). A
Poiseuille flow is imposed at the inlet and outlet with a constant
maximum flow rate of $U_{\max}$. We initialize a semipermeable vesicle
with $\alpha = 0.65$ that spans $10 \mu$m of the total channel width and
investigate the effects of the membrane permeability to water and the
maximum flow velocity on whether a vesicle can successfully pass through
the slit. We color the vesicle according to the sign of its flux---red
for influx and blue for efflux.

@@
